### 2015-02-25 writing/F'14 paper/quantifiers.tex
Paper presentation overhaul.

\paragraph{Experiments}
Our experimental data consist of pairs of sentences generated from a
small artificial grammar. Each sentence contains a quantifier, a noun
which may be negated, and an intransitive verb which may be
negated. We use the basic quantifiers \ii{some}, \ii{most}, \ii{all},
\ii{two}, and \ii{three}, and their negations \ii{no}, \ii{not-all},
\ii{not-most}, \ii{less-than-two}, and \ii{less-than-three}. We also
include five nouns, four intransitive verbs, and the negation symbol
\ii{not}. In order to be able to define relations between sentences
with differing lexical items, we define the lexical relations between
each noun--noun pair, each verb--verb pair, and each
quantifier--quantifier pair. The grammar accepts aligned pairs of
sentences of this form and calculates the natural logic relationship
between them.  Some examples of these data are provided in (\ref{p1}--\ref{p3}) below.
  As in previous sections, the goal of
learning is then to assign these relational labels accurately to
unseen pairs of sentences.

@@

\vspace{-0.6cm}
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natfor  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}\vspace{-0.8cm}

In addition to the two models under study, we also train a summing neural network as a baseline, 
which is identical to the RNN, except that instead of learning a parametric composition function,
it simply sums the word vectors in a sentence to compose them. This baseline model does not
use word order information, though the highly consistent sentence structure in this experiment means
that it can potentially distinguish any two valid sentences except in case the two differ only in the placement of the word \ii{not}, potentially introducing errors into the 58.8\% of examples that contain a sentence with a single
instance of \ii{not}.

\begin{table}[tp]
  \centering
  \begin{tabular}{ l r@{ \ }r r@{ \ }r r@{ \ }r }
    \toprule
    ~ & \multicolumn{2}{c}{25d SumNN} & \multicolumn{2}{c}{25d RNN}  & \multicolumn{2}{c}{25d RNTN}\\
    \midrule
    Train &	96...&	(95...)&	\textbf{100}&		\textbf{(100)}&	99.5&	(99.3)\\	
    Test & 90...&	(80...)&	\textbf{99.4}&\textbf{(99.5)}& \textbf{99.4} & (99.2)\\
    \bottomrule
  \end{tabular}
  \caption{Performance on the quantifier experiments, given as \% correct and macroaveraged F1. The most frequent class, $\natind$, appears in 35.4\% of examples.}
  \label{qresultstable}
\end{table} 
% TODO: Fill in baseline results

%
% do not allow a blank line --- adds too much space
%
\paragraph{Results} The results, reported in Table~\ref{qresultstable}, show that both recursive models are able to learn to generalize the underlying logic satisfactorily, and that the baseline model generalizes well but far from perfectly. We did not observe any consistent pattern in the few errors made by either model, and errors did not tend to be consistent across runs of the experiment, suggesting that there is no fundamental obstacle to learning a perfect model for this problem.

>>>>

\paragraph{Experiments}
Our experimental data consist of pairs of sentences generated
from a grammar for a simple English-like artificial language.
Each sentence contains a quantifier, a noun
which may be negated, and an intransitive verb which may be
negated. We use the basic quantifiers \ii{some}, \ii{most}, \ii{all},
\ii{two}, and \ii{three}, and their negations \ii{no}, \ii{not-all},
\ii{not-most}, \ii{less-than-two}, and \ii{less-than-three}. We also
include five nouns, four intransitive verbs, and the negation symbol
\ii{not}. In order to be able to define relations between sentences
with differing lexical items, we define the lexical relations between
each noun--noun pair, each verb--verb pair, and each
quantifier--quantifier pair. The grammar generates pairs of
sentences of this form and calculates the relations holding
between them.  Some examples of these data are provided in (\ref{p1}--\ref{p3}) below.

@@

\vspace{-0.6cm}
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natfor  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}

We use the same summing baseline as in the previous section.
The highly consistent  sentence structure in this experiment means
that that model can potentially distinguish two valid sentences unless they
 differ only in the placement of the word \ii{not}, potentially introducing errors into 
the 58.8\% of examples that contain a sentence with a single
instance of \ii{not}.

\begin{table}[tp]
  \centering\small
    \begin{tabular}{ l r@{ \ }r r@{ \ }r }

    \toprule
    ~ & \multicolumn{2}{c}{Train} & \multicolumn{2}{c}{Test} \\
    \midrule
    $\natind$ only &	35.4 & (7.5)	& 35.4	& (7.5)\\
    25d SumNN	&	96...&	(95...)&	90...&	(80...)\\	
    25d TreeRNN	&	\textbf{100}&	\textbf{(100)}&	99.5&	(99.3)\\
    25d TreeRNTN	&	\textbf{99.4}&\textbf{(99.5)}&	\textbf{99.4} & (99.2)\\
    \bottomrule
  \end{tabular}

  \caption{Performance on the quantifier experiments, given as \% correct and macroaveraged F1.}
  \label{qresultstable}
\end{table} 
% TODO: Fill in baseline results

%
% do not allow a blank line --- adds too much space
%
\paragraph{Results} The results, reported in Table~\ref{qresultstable}, show that both recursive models are able to learn to generalize the underlying logic satisfactorily, and that the baseline model generalizes well, but far from perfectly. We did not observe any consistent pattern in the few errors made by either model, and errors did not tend to be consistent across runs of the experiment, suggesting that there is no fundamental obstacle to learning a perfect model for this problem.

### 2015-02-25 writing/F'14 paper/recursion.tex
Paper presentation overhaul.

\section{Recursive structure}\label{sec:recursion}

% TODO: Check on citation for clark/coecke/sadr 2011

% Run baseline anyway?

% TODO: Clean up next sent.
Recursive compositional structure is a prominent feature of natural language. 
This section examines the 
question of whether our models are able to learn a 
compositional semantics over such recursive structures.
In our evaluations, we exploit the fact that our logical language
is infinite by testing on strings that are longer and more complex
than any seen in training.

@@

\paragraph{Experiments}
As in \S\ref{sec:join}, we test this phenomenon within the
framework of natural logic, but we now replace the unanalyzed symbols
from that experiment with complex formulae. These formulae
represent a truth-functionally complete classical propositional logic:
each atomic symbol is a variable over the domain \{$\True$, $\False$\}, and the only
operators are truth-functional ones.  Table~\ref{tab:pl} defines this
logic, and Table~\ref{tab:plexs} gives some examples of relational
statements that we can make in these terms. To compute these relations
between statements, we exhaustively enumerate the sets of assignments
of truth values to propositional variables that would satisfy each of
the statements, and then we convert the set-theoretic relation between
those assignments into one of the seven relations in
Table~\ref{b-table}. As a result, each relational statement represents
a valid theorem of the propositional logic.

@@

Socher et al.~\shortcite{socher2012semantic} show that a matrix-vector RNN
model somewhat similar to our RNTN can learn boolean logic, 
a logic where the atomic symbols are simply the
values $\True$ and $\False$. While learning the operators of that logic is not trivial, the outputs of
each operator can be represented accurately by a single bit.
In the more demanding task presented here, the atomic symbols are variables over these values, and the sentence vectors must thus be able to distinguish up to $2^{64}$ distinct conditions on valuations. Relational expressions between these conditions are essentially theorems of propositional logic, and to succeed, the model must learn to approximate the behavior of a theorem prover.
% TODO: Condense this para, and move bulk to footnote.

@@

In order to test the model's generalization to unseen structures, we discard
training examples with more than 4 connectives, yielding 60k short training examples,
and 21k test examples containing up to 12 connectives.
We evaluated both the RNN and RNTN\footnote{We did not run any strictly simpler baselines for this experiment because it is demonstrably impossible to perform substantially above chance on longer expressions without word order information.} on the resulting data, initializing the model parameters randomly,
including the vector representations of the six variables.

\begin{figure*}[t]
  \centering
  \includegraphics[width=5.75in]{decayfig.eps}
%  \includegraphics[width=5.3in]{recursion\string_pairwise.eps}
  \caption{Model performance on propositional logic, by expression size.}
%    The dashed line indicates that only expressions of size four or less appeared in the training data. \textbf{Bottom:} Semantically distinct formulae should have different
%    representations. As measured by Euclidean distance, only the RNTN
%    achieves this for formulae containing more than a small number of
%    connectives (\ii{and} in this example). The RNN quickly collapses the representations,
%    failing to capture the meaning contrasts.

@@

\paragraph{Results} Figure~\ref{prop-results} shows the relationship
between test accuracy and statement length. We found that both 
models were able to perform well on unseen small test examples, 
with RNN accuracy above
98\% and RNTN accuracy above 99\% on formulae below length five.
Starting at size four, performance gradually falls with increasing
size. Training accuracy was 99.4\% for the RNN and 99.8\% for the RNTN.

The performance of these models on small unseen test examples
indicates that they learned correct approximations of the underlying
logic. These approximations are accurate enough to yield
correct answers when the composition layer is only applied a small
number of times, but that the error in the approximation grows with
increasing expression size, resulting in gradually dropping performance. 
Though imperfect, model performance on the long examples is striking. 
The RNTN classifies true examples of every class but $\nateq$ 
(which occurs only once) correctly the majority of the time, where a 
typical statement might be $( ( p_1  \pland ( p_2 \plor ( \plneg p_4 ) ) ) \plor p_3 ) \natcov ( \plneg ( ( \plneg ( ( \plneg ( p_4 \plor p_3 ) )  \plor ( ( \plneg p_3 ) \plor ( \plneg p_3 ) ) ) ) \pland ( \plneg ( ( \plneg ( ( \plneg p_3 ) \plor ( \plneg p_4 ) ) ) \plor ( \plneg p_2 ) ) ) ) )$.
% TODO: Better present examples.

It appears that the RNTN model overfit somewhat relative to the plain RNN,
performing better on the training data and short examples, but worse on longer
examples. Two factors are likely involved in this: even with the lower dimension,
the RNTN composition function has about eight times as many parameters as the
RNN, and thus more capacity to find a solution involving a large number of narrow 
generalizations that work on the training data but don't generalize well. In addition,
the RNTN used here has slightly weaker L2 regularization than the 
RNN ($\lambda_{\textit{RNN}} = 0.001$, $\lambda_{\textit{RNTN}} = 0.0003$). This
yielded better average performance, but may have facilitated this effect.

% \mynote{In an effort to better understand why model performance decays, 
%we evaluated both models on pairs of long formulae involving
%binary connectives, to assess how well they distinguish representations for semantically distinct
%formulae. We found that only the RNTN is able to learn
%substantially different representations for pairs of differing formulae like $(a \pland (a \pland a))$
% and $(a \pland (a \pland b))$ when the difference between the two is placed under multiple operators.
%The RNN separates the bare symbols by a euclidean distance of 3.5, but this falls to less than one once the two are placed under three operators, and quickly approaches zero as depth increases.
% The RNTN separates the bare symbols by 2.5, and this falls off much more gradually to 1.3 with twelve operators.}

% we discovered that this model looses information about in longer
% statements in a particularly problematic way. It appears that that
% model is unable to distinguish between two sentences when the only
% difference between those sentences is embedded within a very deep
% structure. We evaluated both models on sentences that differed in only
% one term, but for which that one term was embedded under a large
% number of conjunctions, such as the pair \ii{a (and a)} and \ii{a (and
%   b)}, or the pair \ii{a (and (a (and a)))} and \ii{a (and (a (and
%   b)))}. We then measured the Euclidean distance between the vector
% representations of the two sentences in each pair. Our findings are
% shown in Figure~\ref{prop-falloff}, and show that while the RNTN can
% distinguish the two sentences well at every size that we test, the RNN
% fails after a depth of approximately six.

>>>>

\section{Recursive structure}\label{sec:recursion}
% TODO: Enter baseline results, use [[Tree]]RNN.

% TODO: Clean up next sent.
Recursive structure is a prominent feature of natural language. 
This section examines the degree to which our models are able to learn a 
compositional semantics over recursive structures.
In our evaluations, we exploit the fact that our logical language
is infinite by testing on strings that are longer and more complex
than any seen in training.

@@

\paragraph{Experiments}
As in \S\ref{sec:join}, we test this phenomenon on data generated from a logic,
 but we now replace the unanalyzed symbols
from that experiment with complex formulae. These formulae
represent a truth-functionally complete classical propositional logic:
each atomic symbol is a variable over the domain \{$\True$, $\False$\}, and the only
operators are truth-functional ones.  Table~\ref{tab:pl} defines this
logic, and Table~\ref{tab:plexs} gives examples of the some of the shorter relational
statements that we generate from it as train and test data. To compute these relations
between statements, we exhaustively enumerate the sets of assignments
of truth values to propositional variables that would satisfy each of
the statements, and then we convert the set-theoretic relation between
those assignments into one of the seven relations in
Table~\ref{b-table}. As a result, each relational statement represents
a valid theorem of the propositional logic, and and to succeed, the models 
must learn to reproduce the behavior of a theorem prover.\footnote{
Socher et al.~\shortcite{socher2012semantic} show that a matrix-vector TreeRNN
model somewhat similar to our TreeRNTN can learn boolean logic, 
a logic where the atomic symbols are simply the
values $\True$ and $\False$. While learning the operators of that logic is not trivial, the outputs of
each operator can be represented accurately by a single bit.
In the more demanding task presented here, the atomic symbols are variables over these values, and the sentence vectors must thus be able to distinguish up to $2^{64}$ distinct conditions on valuations.}

@@

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=5.75in]{decayfig.eps}
%  \includegraphics[width=5.3in]{recursion\string_pairwise.eps}
  \caption{Model performance on propositional logic, by expression size.}
%    The dashed line indicates that only expressions of size four or less appeared in the training data. \textbf{Bottom:} Semantically distinct formulae should have different
%    representations. As measured by Euclidean distance, only the TreeRNTN
%    achieves this for formulae containing more than a small number of
%    connectives (\ii{and} in this example). The TreeRNN quickly collapses the representations,
%    failing to capture the meaning contrasts.

@@

In order to test the model's generalization to unseen structures, we discard
training examples with more than 4 connectives, yielding 60k short training examples,
and 21k test examples containing up to 12 connectives.
We evaluated both the TreeRNN and TreeRNTN on the resulting data, initializing the model parameters randomly,
including the vector representations of the six variables. 
As a baseline, we also train a summing neural network
which is largely identical to the TreeRNN, except that instead of learning a parametric composition function,
it simply sums the term vectors in each expression to compose them. Unlike the two models under study,
whose ability to accurately simulate the logic is an open question, this baseline does not use word order,
and is as such guaranteed to ignore some information that it would need to succeed perfectly.

% TODO: Insert baseline result.
\paragraph{Results} Fig.~\ref{prop-results} shows the relationship
between test accuracy and statement length. BASELINE BASELINE
 BASELINE BASELINE BASELINE BASELINE BASELINE BASELINE BASELINE   We found that both 
models were able to perform well on unseen small test examples, 
with TreeRNN accuracy above
98\% and TreeRNTN accuracy above 99\% on formulae below length five.
Starting at size four, performance gradually falls with increasing
size. Training accuracy was 99.4\% for the TreeRNN and 99.8\% for the TreeRNTN.

The performance of these models on small unseen test examples
indicates that they learned correct approximations of the underlying
logic. These approximations are accurate enough to yield
correct answers when the composition layer is only applied a small
number of times, but that the error in the approximation grows with
increasing expression size, resulting in gradually dropping performance.

It appears that the TreeRNTN model overfit somewhat relative to the plain TreeRNN,
performing better on the training data and short examples, but worse on longer
examples. Two factors are likely involved in this: even with the lower dimension,
the TreeRNTN composition function has about eight times as many parameters as the
TreeRNN, and thus more capacity to find a solution involving a large number of narrow 
generalizations that work on the training data but don't generalize well. In addition,
the TreeRNTN used here has weaker L2 regularization than the 
TreeRNN ($\lambda = 0.0003$ vs. $0.001$). This
yielded better performance averaged across all bins, but may have facilitated this effect.

Though imperfect, model performance on the most difficult set of expressions is nonetheless striking. 
The weaker TreeRNTN classifies true examples of every class but $\nateq$ 
(which is rare in long examples, and occurs only once here) correctly the majority of the time.
% TODO: Better present examples.

% \mynote{In an effort to better understand why model performance decays, 
%we evaluated both models on pairs of long formulae involving
%binary connectives, to assess how well they distinguish representations for semantically distinct
%formulae. We found that only the TreeRNTN is able to learn
%substantially different representations for pairs of differing formulae like $(a \pland (a \pland a))$
% and $(a \pland (a \pland b))$ when the difference between the two is placed under multiple operators.
%The TreeRNN separates the bare symbols by a euclidean distance of 3.5, but this falls to less than one once the two are placed under three operators, and quickly approaches zero as depth increases.
% The TreeRNTN separates the bare symbols by 2.5, and this falls off much more gradually to 1.3 with twelve operators.}

% we discovered that this model looses information about in longer
% statements in a particularly problematic way. It appears that that
% model is unable to distinguish between two sentences when the only
% difference between those sentences is embedded within a very deep
% structure. We evaluated both models on sentences that differed in only
% one term, but for which that one term was embedded under a large
% number of conjunctions, such as the pair \ii{a (and a)} and \ii{a (and
%   b)}, or the pair \ii{a (and (a (and a)))} and \ii{a (and (a (and
%   b)))}. We then measured the Euclidean distance between the vector
% representations of the two sentences in each pair. Our findings are
% shown in Figure~\ref{prop-falloff}, and show that while the TreeRNTN can
% distinguish the two sentences well at every size that we test, the TreeRNN
% fails after a depth of approximately six.

### 2015-02-25 writing/F'14 paper/sick.tex
Paper presentation overhaul.

\section{The SICK textual entailment challenge}

\mynote{NOTE: We might delete this section if we can't improve the numbers in time.}

% TODO: Use ``model not guaranteed to do anything'' rhetoric earlier.
The tree pair model architecture that we use is novel, and though the underlying recursive approach has been validated elsewhere, there is no guarantee that this architecture is suitable for handling inference in the face of the noisy labels and the diverse range of linguistic structures seen in typical natural language data, and our experiments on artificial data alone are not sufficient to address this issue. To investigate the ability of the model to learn on natural data, we train a version of our model on the SICK textual entailment challenge corpus \cite{marelli2014sick}. The corpus consists of about 10k natural language sentence pairs, labeled with \ii{entailment}, \ii{contradiction}, or \ii{neutral}. At only a few thousand distinct sentences (many of them variants on an even smaller set of template sentences), the corpus is not large enough to train a high quality learned model of general natural language, but it is the largest human-labeled entailment corpus that we are aware of.

\begin{table*}[htp]
  \centering\small
  \begin{tabular}{lcl}
    \toprule
A woman is not boiling shrimps.& \ii{contradiction}&	A woman is boiling shrimps.\\
A wild deer is jumping a fence. &\ii{entailment}	&A deer is jumping a fence.\\
A potato is being sliced by a woman. &\ii{entailment}	&A woman is slicing a potato.\\
The plane, which is south African, is flying in a blue sky.& \ii{entailment}&	An airplane is flying through the air.\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofsickdata}Examples of correct RNTN classifications on SICK.}
\end{table*} % TODO: Update. Find incorrect examples?

Adapting to this task required us to make a few additions to the techniques discussed in \S\ref{methods}. In order to better handle rare words, we initialized our word embeddings using 200 dimensional vectors trained with 
GloVe \cite{pennington2014glove} on data from Wikipedia. Since 200 dimensional vectors are too large to be practical in an RNTN on a small dataset, a new embedding transformation layer is needed. Before any embedding is used as an input to a recursive layer, it is passed through an additional $\tanh$ neural network layer with the same output dimension as the recursive layer. This new layer aggregates any usable information from the embedding vectors into a more compact working representation.

@@

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{25d SumNN} & \multicolumn{1}{c}{30d RNN}  & \multicolumn{1}{c}{50d RNTN}\\
    \midrule
    SICK Train &  TODO & 95.4 &  \textbf{97.8}  \\
    DG (Train) &  TODO & 67.0 & \textbf{74.0}  \\
    SICK Test & TODO & 74.9 & \textbf{76.9}  \\
    \bottomrule
  \end{tabular}
  \caption{Performance on collapsed SICK data. The class NEUTRAL appears in 56.7\% of SICK examples and 50\% of DG examples.}
  \label{sresultstable}
\end{table}

The results are shown in Table \ref{sresultstable}. Despite the small amount of high quality training data available and the lack of resources for learning lexical relationships (especially exclusion, as in \ii{cat}--\ii{dog}), it is possible to train our model to perform competitively on textual entailment. Our RNTN did not reach the performance of the winning system (84.6\%), but it did exceed that of eight out of 18 submitted systems, including several which used sophisticated hand-engineered features and lexical resources specific to the version of the entailment task at hand.

@@

% TODO: Better error analysis

@@

>>>>

\section{The SICK textual entailment challenge}\label{sec:sick}

The tree pair model architecture that we use is novel, and though the underlying recursive approach has been validated elsewhere, there is no guarantee that this architecture is suitable for handling inference in the face of the noisy labels and the diverse range of linguistic structures seen in typical natural language data, and our experiments on artificial data alone are not sufficient to address this issue. To investigate the ability of the model to learn on natural data, we train a version of our model on the SICK textual entailment challenge corpus \cite{marelli2014sick}. The corpus consists of about 10k natural language sentence pairs, labeled with \ii{entailment}, \ii{contradiction}, or \ii{neutral}. At only a few thousand distinct sentences (many of them variants on an even smaller set of template sentences), the corpus is not large enough to train a high quality learned model of general natural language, but it is the largest human-labeled entailment corpus that we are aware of.

\begin{table*}[htp]
  \centering\small
  \begin{tabular}{lcl}
    \toprule
Analysis\\
Analysis\\
Analysis\\
Analysis\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofsickdata}Examples of correct TreeRNTN classifications on SICK.}
\end{table*} % TODO: Update. Find incorrect examples?

Adapting to this task required us to make a few additions to the techniques discussed in \S\ref{methods}. In order to better handle rare words, we initialized our word embeddings using 200 dimensional vectors trained with 
GloVe \cite{pennington2014glove} on data from Wikipedia. Since 200 dimensional vectors are too large to be practical in an TreeRNTN on a small dataset, a new embedding transformation layer is needed. Before any embedding is used as an input to a recursive layer, it is passed through an additional $\tanh$ neural network layer with the same output dimension as the recursive layer. This new layer aggregates any usable information from the embedding vectors into a more compact working representation.

@@

\begin{table}[tp]
  \centering \small
  \begin{tabular}{ l r@{ \ } r@{ \ } r@{ \ } }
    \toprule
    ~&\multicolumn{1}{c}{SICK Train} & \multicolumn{1}{c}{DG Train}  & \multicolumn{1}{c}{SICK Test}\\
    \midrule
    NEUTRAL only &	56.7	&	50.0	  &	56.7\\
    25d SumNN	&	TODO	&	TODO &	TODO	\\
    30d TreeRNN	&	95.4		&	67.0	&	74.9		\\
    50d TreeRNTN	&\textbf{97.8}	& \textbf{74.0}&\textbf{76.9}\\
    \bottomrule
  \end{tabular}
  \caption{Classification accuracy for SICK.}
  \label{sresultstable}
\end{table}

The results are shown in Table \ref{sresultstable}. Despite the small amount of high quality training data available and the lack of resources for learning lexical relationships (especially exclusion, as in \ii{cat}--\ii{dog}), it is possible to train our model to perform competitively on textual entailment. Our TreeRNTN did not reach the performance of the winning system (84.6\%), but it did exceed that of eight out of 18 submitted systems, including several which used sophisticated hand-engineered features and lexical resources specific to the version of the entailment task at hand.

@@

% TODO: Update analysis

@@

ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
ANALYSIS\\
